Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-09 chapters/introduction/introduction.tex
some more background

\section{Our Approach}
Our approach consists of two big steps. First, we propose a general
probabilistic model to jointly estimate the geo-calibration
parameters. The key for the success of this model is to construct good
constraint functions which describe the fitness between the calibration
parameters and the images. As the second step of our approach, we
dismantle the full geo-calibration into several partial
geo-calibration tasks, each of which could provides a strong constraint
function that fit in the general model. The architecture of
our approaches refers to
\figref{intro:architecture}.

\subsection{General Probabilistic Model for Geo-Calibration}
The complete camera geo-calibration detects the camera
geographic location, pose, and focal length of the camera.  We
design a general model to estimate the probability over these
geo-calibration parameters: First, we model the relation between the
image projection of the scene and the geo-calibration parameters. This
relation is ruled by both the pin-hole model principle and the
geographic location of the camera.
We then construct a scoring function to measure the ``fitness'' between the
calibration parameters and the observation of the image. 
The scoring function is proportional to the probability distribution
of the camera parameters. We propose a Markov Chain Monte
Carlo (MCMC) sampling approach to approximate the underlying
probability distribution over the full geo-calibration of the camera.
Our model is a general architecture, which can take different
constraints to form the scoring function. The details about this model
can be found in \chapref{mcmc}.

\subsection{Developing Constraint Functions}
In our general model, the scoring function is defined as a linear
combination of multiple constraint functions.
In the rest of the work, We focus on developing good constraint
functions for different set of calibration parameters. Besides, we
also show our methods are able to extract high-level image features
with the help of geographic information.

@@

>>>>

\section{\todo{Dataset}}
Introduce the dataset we use.

\section{Our Approach}
Our approach consists of two big steps. First, we propose a general
probabilistic model to jointly estimate the geo-calibration
parameters. The key for the success of this model is to construct good
constraint functions which describe the fitness between the calibration
parameters and the images. As the second step of our approach, we
dismantle the full geo-calibration into several partial
geo-calibration tasks, each of which could provides a strong constraint
function that fit in the general model. The architecture of
our approaches refers to \figref{intro:architecture}.
%
In the end, we show that learning to geo-calibrate a camera is helpful
for high-level image feature extracting.

\subsection{General Probabilistic Model for Geo-Calibration}
The complete camera geo-calibration detects the camera
geographic location, pose, and focal length of the camera.  We
design a general model to estimate the probability over these
geo-calibration parameters: First, we model the relationship between the
image projection of the scene and the geo-calibration parameters. This
relationship can be described by the pin-hole model, and
the geographic location of the camera.
We then construct a scoring function to measure the ``fitness'' between the
calibration parameters and the observation of the image. 
The scoring function is proportional to the probability distribution
of the camera parameters. We propose a Markov Chain Monte
Carlo (MCMC) sampling approach to approximate the underlying
probability distribution over the full geo-calibration of the camera.
Our model is a general architecture, which can take different
constraints to form the scoring function. The details about this model
can be found in \chapref{mcmc}.

\subsection{Developing Constraint Functions}
In our general model, the scoring function is defined as a linear
combination of multiple constraint functions.
In the rest of the work, we focus on developing good constraint
functions for different set of calibration parameters.

@@

\section{Geo-Calibration for Feature Learning}
